moderated_regressions

### 2024-05-14 moderated_regressions.Rmd
Adding interaction graphs

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(chal.2.eng, paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

#paste(round(hr_eng_m3_r,2),"**")

@@

papaja::apa_table(regtable,
                 escape=FALSE,
                 note="* = p < .05; ** = p < .01")

#https://stackoverflow.com/questions/67088456/r-aligning-table-content-to-decimal-points-in-kable

#tribble(
#  ~Variable_1,~Variable_2,
#  "13.5","4.4**",
#  "12.7***","1.2*",
#  "0.4","0.3***",
#  "2.3**","11.5**"
#)%>%
#  rename_all( ~ str_c("{ ",.," }"))%>%
#  kable(format = "latex", booktabs=T, escape = T)%>%
#  kable_styling(position = "center", latex_options = "hold_position")
```

@@

>>>>

DV <- c("Engagement","","", "Stress","","", "Burnout","","")
Step <- c("1", "","2", "1", "","2", "1", "","2")
Model <- c("Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource", "Challenge", "Resource", "Challenge X Resource")
Beta <- c(sigfill(chal.2.eng), paste(res.2.eng,"**"), paste(int.cr.3.eng,"*"), chal.2.stress, res.2.stress, int.cr.3.stress, paste(chal.2.burn,"**"), res.2.burn, int.cr.3.burn)
R2 <- c("", paste(cr_eng_m2_r,"**"), paste(cr_eng_m3_r,"**"), "", round(cr_stress_m2_r,2), round(cr_stress_m3_r,2), "", paste(round(cr_burn_m2_r,2),"**"), paste(round(cr_burn_m3_r,2),"**"))
DeltaR <- c("","", paste(cr_eng_r_square_change,"*"), "","",cr_stress_r_square_change, "","",cr_burn_r_square_change)

@@

@@

```{r fig.cap="Interaction between Challenge and Resources on Engagement"}
#install.packages("interactions")
library(interactions)

#running it with unstandardized bs here. 
cr_eng_m3u <- lm(engagement ~ overall.challenge_center + overall.resource_center + overall.challenge_center*overall.resource_center, data = data)
summary(cr_eng_m3u)

cr_eng_plot <- interact_plot(cr_eng_m3u, pred = overall.challenge_center, modx = overall.resource_center, interval = TRUE,
              int.width = 0.8)
cr_eng_plot
```

```{r fig.cap="Interaction between Hindrances and Resources on Stress"}
#install.packages("interactions")
library(interactions)

hr_stress_m3u <- lm(stress ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_stress_m3u)

hr_stress_plot <- interact_plot(hr_stress_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
              int.width = 0.8)
hr_stress_plot
```

```{r fig.cap="Interaction between Hindrances and Resources on Burnout"}
#install.packages("interactions")
library(interactions)

hr_burn_m3u <- lm(burnout ~ overall.hindrance_center + overall.resource_center + overall.hindrance_center*overall.resource_center, data = data)
summary(hr_burn_m3u)

hr_burn_plot <- interact_plot(hr_burn_m3u, pred = overall.hindrance_center, modx = overall.resource_center, interval = TRUE,
              int.width = 0.8)
hr_burn_plot
```
